Optimal Fitting of Planar Curves to Prescribed Constraints

### 2013-08-31 idp/documentation/paper.tex
introduced description and description language

			We conclude that the two ways in which curve design software can affect the design process are through the choice of specification language and fairness measure. Ideally, the specification language should be very expressive, yet easy to handle for humans, enabling the user to communicate their intent to the software efficiently. The fairness should capture the intuitive notion of curve smoothness sufficiently well. These goals are competing with the software's ability to derive curves from specifications and the fairness measure reliably and efficiently, a process which becomes increasingly difficult with more expressive specification languages and more complex fairness measures.

@@

				In existing vector graphics software, Bézier splines are edited by more or less directly modifying the coefficient points of the underlying Bézier curves. In the case of cubic Bézier curves, the first and the last coefficient points represent the curve's start and end points, while the differences between the second and the first as well as the fourth and the third coefficient points are proportional to the velocity of the curve at the start and end points, respectively. In that sense, the user can specify start end end points of the curve, as well as start and end velocities of the curve using the coefficient points. Most vector graphics tools have functions that allow preserving the \(G^1\) continuity of the spline by automatically modifying adjacent coefficient points accordingly. They usually do not ensure \(\mathrm{G}^2\) continuity though. Some tools can also modify existing coefficient points in such a way that the curve passes through a point that is chosen by the user without adding more Bézier curves to the spline.

@@

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{../resources/usability_bezier.pdf}
					\caption{Usability Analysis of Bézier Splines (left: \cite{Fluttershy}, right: \cite{Lugia})}
					\label{figure:usability_bézier}
				\end{figure}

				% TODO: improve example index numbers
				Figure \ref{figure:usability_bézier} illustrates some of these issues by showing some examples of Bézier splines as they appear in common design tools. Bézier nodes are displayed as filled dots, while Bézier handles are displayed as circles.

@@

		\subsection{Specification-Based Curves}
		\label{section:specification-based_curves}

			Seeing how the specification language and fairness measure almost completely determine all usability aspects of the resulting curve design tool, it seems unwise to choose them based on low-level mathematical aspects of the curve as is the case with Bézier splines. Spiro splines are much better in that a lot of effort was put into the fairness measure. Unfortunately, the project has set out to solve the problem of constructing interpolating splines, thereby committing to a very restricted specification language right from the start.

			We think that in order to get the best usability, using a good specification language which does not rely on implementation details has to be the top priority. Together with a good fairness measure, it will then lead to usable curve design tools. Since it is not immediately clear which specification language or which fairness measure is the best, the first step is to move away from the traditional explicit curve construction, and instead use a process that enables the creation of curves based on explicit specifications and a fairness measure.

			\begin{figure}[htb]
				\centering
				\includegraphics[width=\textwidth]{../resources/specification-based_curves.pdf}
				\caption{Specification-Based Curves}
				\label{figure:specification-based_curves}
			\end{figure}

			Figure \ref{figure:specification-based_curves} shows such a process. Note that many specifics are still left undetermined in this approach since the previous usability analysis didn't give a complete answer as to what the optimal curve design tool looks like. It has yet to be determined what the specification language and fairness measure should be, whether to do segmentation (spline approach) or use a single curve, or if the curve should be determined by numerical optimization or by explicit construction.

@@

		\subsection{Specification Language and Fairness Measure}
		\label{section:specification_language_fairness_measure}

			After using the results of the usability analysis to establish the general approach to curve design tools in section \ref{section:specification-based_curves}, it's time to decide on the specifics in order to create an instance of this model. The first steps are to choose both a specification language and a fairness measure.

@@

		\subsection{Nonlinear Optimization on Polynomial Curves}
		\label{section:nonlinear_optimization_polynomial_curves}

			Having decided on a specification language and a fairness measure in section \ref{section:specification_language_fairness_measure}, the only thing missing from the process described in section \ref{section:specification-based_curves} is a way of turning specifications into actual curves. In order to achieve this goal, we decided to use nonlinear optimization on polynomial splines, that is, the curves are splines built from parametric polynomial curves whose parameters are determined using nonlinear optimization based on the specification and the fairness measure.

@@

				In the following sections, we will introduce the optimization goals that enable us to use nonlinear optimization for building curves based on specifications using the specification language and fairness measure established in section \ref{section:specification_language_fairness_measure}. We will also state how they are expressed using constraint function and bounds as well as objective function.

>>>>

			% TODO: properly instroduce description language, how the fairness measure determines semantics but not syntax of that language, etc., figure out when to use description and when to use specification, since they are syntactically identical
			We conclude that the two ways in which curve design software can affect the design process are through the choice of specification language and fairness measure, which we will call the description language. The usability is of course also affected by the software's ability to derive curves from descriptions.

			Ideally, the specification language should be very expressive, yet easy to handle for humans, enabling the user to communicate their intent to the software efficiently. The fairness should capture the intuitive notion of curve smoothness sufficiently well. These goals are competing with the software's ability to derive curves from descriptions reliably and efficiently, a process which becomes increasingly difficult with more expressive specification languages and more complex fairness measures.

@@

				% TODO: explain velocity
				In existing vector graphics software, Bézier splines are edited by more or less directly modifying the coefficient points of the underlying Bézier curves. In the case of cubic Bézier curves, the first and the last coefficient points represent the curve's start and end points, while the differences between the second and the first as well as the fourth and the third coefficient points are proportional to the velocity of the curve at the start and end points, respectively. In that sense, the user can specify start end end points of the curve, as well as start and end velocities of the curve using the coefficient points. Most vector graphics tools have functions that allow preserving the \(G^1\) continuity of the spline by automatically modifying adjacent coefficient points accordingly. They usually do not ensure \(\mathrm{G}^2\) continuity though. Some tools can also modify existing coefficient points in such a way that the curve passes through a point that is chosen by the user without adding more Bézier curves to the spline.

@@

				% TODO: consider moving away from the 'source image is traced' samples and use the actual vector graphics leading to those curves
				% TODO: make sure the size of the node visualization is consistent, use visible colors for node visualization, maybe get rid of circles for handles
				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{../resources/usability_bezier.pdf}
					\caption{Usability Analysis of Bézier Splines (left: \cite{Fluttershy}, right: \cite{Lugia})}
					\label{figure:usability_bézier}
				\end{figure}

				% TODO: improve example index numbers (also use font consistent with text)
				Figure \ref{figure:usability_bézier} illustrates some of these issues by showing some examples of Bézier splines as they appear in common design tools. Bézier nodes are displayed as filled dots, while Bézier handles are displayed as circles.

@@

		\subsection{Description-Based Curves}
		\label{section:description-based_curves}

			Seeing how the description language almost completely determine all usability aspects of the resulting curve design tool, it seems unwise to choose them based on low-level mathematical aspects of the curve as is the case with Bézier splines. Spiro splines are much better in that a lot of effort was put into the fairness measure. Unfortunately, the project has set out to solve the problem of constructing interpolating splines, thereby committing to a very restricted specification language right from the start.

			We think that in order to get the best usability, using a good specification language which does not rely on implementation details has to be the top priority. Together with a good fairness measure, it forms a description language that, if it allows for reliable and efficient derivation of curves, will then lead to usable curve design tools. Since it is not immediately clear which description language is the best, the first step is to move away from the traditional explicit curve construction, and instead use a process that enables the creation of curves based on descriptions.

			\begin{figure}[htb]
				\centering
				\includegraphics[width=\textwidth]{../resources/description-based_curves.pdf}
				\caption{Description-Based Curves}
				\label{figure:description-based_curves}
			\end{figure}

			Figure \ref{figure:description-based_curves} shows such a process. Note that many specifics are still left undetermined in this approach since the previous usability analysis didn't give a complete answer as to what the optimal curve design tool looks like. It has yet to be determined what the description language should be, as well as how to derive curves from them.

@@

		\subsection{Description Language}
		\label{section:description_language}

			After using the results of the usability analysis to establish the general approach to curve design tools in section \ref{section:description-based_curves}, it's time to decide on the specifics in order to create an instance of this model. The first steps are to choose both a specification language and a fairness measure.

@@

		\subsection{Curve Derivation}
		\label{section:curve_derivation}

			Having decided on a specification language and a fairness measure in section \ref{section:description_language}, the only thing missing from the process described in section \ref{section:description-based_curves} is a way of turning specifications into actual curves. In order to achieve this goal, we decided to use nonlinear optimization on polynomial splines, that is, the curves are splines built from parametric polynomial curves whose parameters are determined using nonlinear optimization based on the specification and the fairness measure.

@@

				In the following sections, we will introduce the optimization goals that enable us to use nonlinear optimization for building curves based on specifications using the specification language and fairness measure established in section \ref{section:description_language}. We will also state how they are expressed using constraint function and bounds as well as objective function.
